### 2019-09-25 reports/thesis/book.tex

Voids in the order of millimetres were detectable using this method. Further work could include test samples made from materials such as titanium alloys (Ti-6Al-4V). This can be challenging because artefacts, such as streaks, can appear when using XCT for metal parts \citep{deman1998metal, nawaz2014metal}. Another problem is that because titanium products are created using a power-based method, powder may become trapped \citep{brierley2018optimized} in designed voids. This results in voids appearing with less contrast in the projections, making it harder to detect.

This thesis is a contribution to real-time quality control for AM. A powerful multi-core computer could be used to conduct the statistical analysis on a few x-ray projections of AM products on a conveyor belt. By using fewer projections, quality control can be faster which advances the development, and increases the scope of applications, of AM.

>>>>

Voids in the order of millimetres were detectable using this method. Further work could include test samples made from materials such as titanium alloys (Ti-6Al-4V). This can be challenging because artefacts, such as streaks, can appear when using XCT for metal parts \citep{deman1998metal, nawaz2014metal}. Another problem is that because titanium products are created using a power-based method, the powder may become trapped \citep{brierley2018optimized} in designed voids. This results in voids appearing with less contrast in the projections, making it harder to detect.

This thesis is a contribution to real-time quality control for AM. A powerful multi-core computer could be used to conduct the statistical analysis on a few x-ray projections of AM products on a conveyor belt. By using fewer projections, quality control can be faster which advances the development and increases the scope of applications of AM.

### 2019-09-25 reports/thesis/chapters/1_literatureReview.tex

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{../figures/literatureReview/literature_stl.png}
  \caption{An example of a CAD model (left) converted to a STL file (right). Republished with permission of Springer New York, from \cite{gibson2010additive}; permission conveyed through Copyright
Clearance Center, Inc.}
  \label{fig:literature_stl}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{../figures/literatureReview/literature_angles.png}
  \caption{A reconstruction when scanning three aligned balls using a different number angular projections. Reprinted from \cite{kruth2011computed}\textsuperscript{\textcopyright} with permission from Elsevier.}
  \label{fig:literature_angles}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{../figures/literatureReview/literature_stl.png}
  \caption{An example of a CAD model (left) converted to an STL file (right). Republished with permission of Springer New York, from \cite{gibson2010additive}; permission conveyed through Copyright
Clearance Center, Inc.}
  \label{fig:literature_stl}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{../figures/literatureReview/literature_angles.png}
  \caption{A reconstruction when scanning three aligned balls using a different number of angular projections. Reprinted from \cite{kruth2011computed}\textsuperscript{\textcopyright} with permission from Elsevier.}
  \label{fig:literature_angles}
\end{figure}
